---
title: "Mapping SNFs and Episodes"
output: html_notebook
---

# Introduction:

In this number of SNFs and number of cases per month will plotted on the maps. Required packages are loaded below:



```{r}
library(ggplot2)
library(ggmap)
library(tidyverse)
library(tidyverse)
library(ggplot2)
library(zipcode)
library(tidyverse)
library(maps)
library(viridis)
library(ggthemes)
library(readr)
library(timetk)
library(lubridate)
library(maps)

library(gganimate)
library(gifski)
library(transformr)

library(readr)
library(readxl)

```


# Import Data:

```{r}

merged_data <- read_csv("../data/merged_data.csv")
CCs_SNFs <- read_excel("../data/CCs_SNFs.xlsx")
CCs <- read_excel("../data/CCs.xlsx")
SNFs <-read_excel("../data/SNFs.xlsx") 
Episodes <-read_excel("../data/Episodes.xlsx") 
```



Let's take a look at the datasets:

```{r}
head(merged_data)
head(CCs)
```




For initial purpose visualization will be done on googlemaps. Note that to use the chunk below use needs to use their own googlemaps API.

```{r}
google_map_token <- readRDS(file = "D:/Workspace AOT/AoTEXPLORE/Vanderbilt_EDA/data/google_map.rds")

ggmap::register_google(key = google_map_token)
rm('google_map_token')
```





```{r}
p <-  qmap()


p <- ggmap(get_googlemap(center = c(lon = -99.9018  , lat = 31.9686),
                    zoom = 6, scale = 4,
                    maptype ='terrain',
                    color = 'color'))
```


Plotting locations of CCs:

```{r}
p+geom_point(aes(Lon,Lat),data = merged_data)
```








For SNFs there are no longitudes and latitudes.However, it can be extracted from zipcodes.


```{r}

data("zipcode")
zipcode

test <- merged_data %>% mutate(ProviderPracticeZipCode=as.character(ProviderPracticeZipCode))
head(merged_data)
character()


merged_zip <- test %>% left_join(zipcode, by = c("ProviderPracticeZipCode" = "zip"))

merged_zip <- merged_zip %>% drop_na(AdmitDate)

merged_zip <- merged_zip %>% mutate(AdmitDate=ymd(AdmitDate))


```





```{r}
p+geom_point(aes(longitude,latitude),data = merged_zip,alpha=.3)
```


It is noticable that some place have high concetration of SNFs and sparse in other places.


```{r}
q <- merged_zip %>% filter(month(AdmitDate)==1) %>% geom_point(aes(longitude,latitude))

summary_intake_snff <- merged_zip %>% group_by(AdmitDate,latitude,longitude) %>% summarise(intake=n())



```
Groups by counties


```{r}



p+geom_point(aes(longitude,latitude,color=intake),data = summary_intake_snff %>% filter(month(AdmitDate)==2),alpha=.3)+scale_color_gradient2(midpoint=30, low="blue", mid="white",
                     high="red", space ="Lab" )
```
This plot is for Februrary only.


# Mapping by Counties:

Since most analysis for this project was done by counties, plots will be made for counties below:

```{r}

state.md <- map_data('state', 'texas')
  md <- map_data('county', 'texas')
```


```{r}
get_plot_data <- function(dataframe,state.md,md){
  mpcPlotData <- dataframe  %>%
  mutate(subregion=tolower(county))

plotData <- left_join(md, mpcPlotData, by="subregion")


return(plotData)
}
```




```{r}


timeseries_base <- read_csv("../data/timeseries_base.csv")

```



```{r}
snf_county <- read_csv("../data/snfs_per_county.csv")

snf_county_plot <- get_plot_data(snf_county,state.md,md)





```

```{r}
ggplot() + 
  geom_polygon(data = snf_county_plot , aes(x=long, y = lat, fill=pid, group = group), color="white") + 
  geom_polygon(data = state.md, aes(x=long, y=lat, group=group), color="black", fill=NA) +
  coord_fixed(1.3) +
  scale_fill_gradient(low = "white", high = "red", na.value="white") 
  

```



```{r}
snf_monthly <- read_csv("../data/county_count_monthly.csv")

snf_monthly_plot <- get_plot_data(snf_monthly,state.md,md)

snf_monthly_plot <- snf_monthly_plot %>% mutate(pid = ifelse(pid >= 25, 25, pid),
                                                episodeid = ifelse(episodeid >= 25, 25, episodeid))



```


Below SNFs are plotted based on monthly cases. The highest value is capped to 25 for visualisation purpose.

```{r}
baseMap <- ggplot() + 
  geom_polygon(data = snf_monthly_plot, aes(x=long, y = lat, fill=pid, group = group), color="white") + 
  geom_polygon(data = state.md, aes(x=long, y=lat, group=group), color="black", fill=NA) +
  coord_fixed(1.3) +
  scale_fill_gradient(low = "white", high = "red", na.value="grey80")
```




```{r}
upgradedMap <- baseMap +
  theme_void() +
  theme(legend.position=c(1.1,.72), legend.text.align=0, plot.title=element_text(hjust=.1, face="bold"), plot.caption=element_text(hjust=0)) 

upgradedMap
```



```{r}


animatedMap <- upgradedMap +
  geom_text(data=snf_monthly_plot, aes(x=-102.413507, y=28.340432, label=as.character(month(month))), check_overlap = TRUE, size=10, fontface="bold") +
  transition_states(month(month), 1, 12)

animatedMap
```









```{r}
mapGIF <- animate(animatedMap) 
anim_save("../data/gifs/map_snff_montly.gif", animation=mapGIF)
```


Below episodes are plotted based on monthly cases. The highest value is capped to 25 again for visualisation purpose.

```{r}
baseMap <- ggplot() + 
  geom_polygon(data = snf_monthly_plot, aes(x=long, y = lat, fill=episodeid, group = group), color="white") + 
  geom_polygon(data = state.md, aes(x=long, y=lat, group=group), color="black", fill=NA) +
  coord_fixed(1.3) +
  scale_fill_gradient(low = "white", high = "red", na.value="grey80")
```




```{r}
upgradedMap <- baseMap +
  theme_void() +
  theme(legend.position=c(1.1,.72), legend.text.align=0, plot.title=element_text(hjust=.1, face="bold"), plot.caption=element_text(hjust=0)) 

upgradedMap
```





```{r}


animatedMap <- upgradedMap +
  geom_text(data=snf_monthly_plot, aes(x=-102.413507, y=28.340432, label=as.character(month(month))), check_overlap = TRUE, size=10, fontface="bold") +
  transition_states(month(month), 1, 12)

animatedMap
```









```{r}
mapGIF <- animate(animatedMap) 
anim_save("../data/gifs/map_episodes_montly.gif", animation=mapGIF)
```









